### 2013-06-26 Tex/chapters/results.tex
kurze Erklärung zu cubic splines

    Therefore a cubic spline interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}

@@

>>>>

    Because  the magnetisation \(m\) is only measured for discrete values
    of \(T\), \(g\) is also only known for these discrete values and has
    to be interpolated to find a intersection. Therefore a cubic spline
    interpolation\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}

@@

    Cubic spline interpolation is a piecewise fitting of polynoms of
    degree three which are joined under the condition to be at least two
    timescontinuously differentiable.
